---
title       : Random Number Generator
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Reasons for using application

1. Many areas need random numbers for sampling done for medical chart audits.
2. It can also be used when trying to test how close random numbers followo their distribution
3. It also shows that random numbers change as you change a seed.

--- .class #id 

## Example Generating Five Random Normal Numbers from a Standard Normal Distribution

```{r}
setwd("C:/Users/slussetc/Documents/GitHub/Developing_Data_Products")
set.seed(200)
rnorm(5,0,1)
```

--- .class #id
## Other things to consider
1. With some slight changes to the code, this could be used to generate random
numbers within a give range.
2.  This can also be used for random number generation from other distributions
3.  Similar functions can be used to get the quantile of distributions

--- .class #id
##  Example of Quantiles
Here is a call that returns the 0.975 quantile of a random normal
```{r}
setwd("C:/Users/slussetc/Documents/GitHub/Developing_Data_Products")
set.seed(200)
qnorm(0.975,0,1)
```

